### 2021-07-15 src/paper/data/course_of_disease.tex
Add values and refer to sections in tables B.2 until B.4. Add paragraph on immunity and infection probability in the course of disease section.

@@

>>>>

% Susceptibility and Infectiousness
 \comment[id=K]{@Janos: read this.}
The first stage of any disease is the infection. As detailed in
Equation~\ref{eq:infection_probability_formula} the infection
probability depends on the contact type, the calendar date to determine the seasonality,
the age group of the susceptible person and the variant the infectious person is
carrying.
%
The base infection probability of each contact type ($\beta_c$) is estimated inside our
model (Section~\ref{subsec:estimated_params}). How we model and set the seasonality is
detailed in Section~\ref{subsec:seasonality}. For the susceptibility of each age group
($\zeta_a$) we take the estimates of \citet{Davies2020} (Extended Data Fig. 4). Lastly,
we calibrate the infectiousness of the B.1.1.7 variant ($\sigma_{B.1.1.7}$) from
\citet{Davies2021} to 1.67.

@@

% Immunity and Vaccination -------------------------------------------------------------

 \comment[id=K]{@Janos: Read this!}

Individuals can become immune either through infection ($\gamma_{immune}$) or vaccination
($\gamma_{vacc,\:d}$). As reinfections are estimated to be extremely rare
\citep{AbuRaddad2020}, we simply set the immunity period to one year with probability
one, i.e. everyone that has been infected enjoys immunity for the rest of the simulation
period.

% vaccinations
The second route to immunity is through vaccination. Germany has mostly relied on the
Pfizer-BioNTech BNT162b2 and Oxford-AstraZeneca ChAdOx1-S vaccines with smaller shares of
the Moderna and Johnson\&Johnson vaccines \citep{Impfdashboard}. As \citet{Pritchard2021}
and \citet{Harris2021} find no difference in the effectiveness between the two most
common vaccines, we do not distinguish between vaccine types.

Immunity is binary in our model, i.e. individuals become either sterile immune or remain
susceptible. Thus, we cannot simply use the reported effectiveness but must also include
the risk of asymptomatic and sub-clinical reinfection among the vaccinated in our
probability to become immune upon vaccination. This is important as there is by now ample
evidence that vaccinated individuals can still get infected with SARS-CoV-2 and transmit
the disease \citep{Petter2021, LevineTiefenbrun2021, Harris2021}.

The reported effectiveness for BNT162b2 is estimated to be 90\% 21 days after the first
shot \citep{Hunter2021}. The effectiveness does not increase much through the booster
shot as \citet{Thompson2021} report 90\% (95\% CI = 68\%–97\%) effectiveness against
PCR-confirmed infections after two doses for mRNA vaccines in general. We therefore do
not distinguish between the first and the booster shot.

On the other hand, \citet{Lipsitch2021} report a lower bound on transmission for
the very similar Moderna vaccine of 61\%.

Taking this evidence together we simplify to 35\% of individuals developing immunity 14
days after their vaccination and 40\% after 21 days. For the remaining 25\% we assume
that the vaccine does not protect them. %
This may seem slightly optimistic for how early vaccinations may already have an effect
when looking at infection rates like \citet{Hunter2021}. However, it can be expected that
individuals underestimate the time it takes for the vaccine to work and behave less
carefully after receiving a vaccination. We err on the side of being too optimistic for
the effectiveness of vaccine and assume a significant protection after 14 days as
\citet{LevineTiefenbrun2021} report strongly reduced viral loads already 12 to 28 days
after the first vaccine.
